---
output: 
  md_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

cityhoods
==========

`cityhoods` is an R package for easy visualization of Finnish city administrative districts. These districts can be of varying sizes: wards, neighbourhoods, boroughs, quarters, et cetera.

## Installation

```{r install, eval = FALSE}
devtools::install_github("pitkant/cityhoods")
```

## Usage

Currently implemented are 2 functions:

- get_areas: downloading maps from the server
- visualize_data: for easy combining of map data with statistical data

Included with the package are 3 datasets from the city of Turku.

```{r example1}
library(cityhoods)
get_areas(city = "turku", level = 1, draw = TRUE)
get_areas(city = "helsinki", level = 2, draw = TRUE)
```

Function for data visualization is currently very much WIP and experimental and works only with level 3 data from city of Turku. Since it contains interactive menu elements it will not be reproduced in this readme, but see and try for yourself!

```{r example2, eval = FALSE}
visualize_data(city = "turku", level = 3, dataset = turku_vaesto_ika_2010_2019)
```